Objectification in Action: Self- and Other-Objectification in Same-gender Interactions

### 2020-07-09 Final_Manuscript.Rmd
small changes closing github issues

While @garcia2016objectification used dyadic path analysis, we will conduct our dyadic analyses using multilevel modeling. Dyadic analyses for distingishable dyads (e.g., mixed-gender interacting pairs) is more natural in Structual Equation Modeling (SEM) than it is for indistinguishable dayds (e.g., same-gender interacting pairs) [@ledermann2017analyzing; @garcia2015moderation]. One reason for this asymmetry is that, due to the arbitrary distinctions made bewteen "partner 1" and "partner 2" in indistinguishable dyads, many estimates need to be fixed to be equal (i.e., paths, variances, covariances, endogenous intercepts, and exogenous means) for indistinguishable dyads but these equality contraints should not then be considered in the degrees of freedom calculations for fit estimations [@olsen2006structural]. Further, @olsen2006structural detail how a new independence model and the corresponding fit measure should be re-calculated for indistinguishable dyads models. The current study uses dyadic multilevel modeling (MLM) to test all relationships and mediation paterns. See @ledermann2017analyzing for a more complete discussion of the considerations for using SEM versus MLM for dyadic analysis.

@@

Before moving to the main analyses, we discuss statistical equivalence test that provide support for combining Sample 1 and Sample 2 in one analysis sample. The online supplemental material contains the main analyses separated by samples.

@@

```{r}
#SSO
apim1 <- gls(howbody_avg_A ~ a2pSOO_A + a2pSOO_P + TSO_A + a2pSOO_P*TSO_A, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

apim1.b <- gls(howbody_avg_A ~ a2pSOO_A + a2pSOO_P + TSO_A, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

summary(apim1)
```
The most important finding from @garcia2016objectification was the significant partner effect of other objectification and SSO (specifically men's objectification of women and women's SSO). As expected, the partner effect of other-objectification on SSO in the current all-women sample was statistically signficant, `r report_stats(apim1, 3)`, replicating @garcia2016objectification's fiding. One's own other objectification had no effect on SSO, `r report_stats(apim1, 2)`. Contrary to past finding however, there was no statistically significant interaction of partner's other objectification and the person's trait self-objectification on SSO, `r report_stats(apim1, 5)`. There was also no significant main effect of trait self-objectification on SSO `r report_stats(apim1.b, 4)`.

```{r}
#authenticity
apim2 <- gls(authenticity_A ~ howbody_avg_A, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

apim2.b <- gls(authenticity_A ~ howbody_avg_A + a2pSOO_P, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

apim2.c <- gls(authenticity_A ~a2pSOO_P, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

```{r}
#cognitive performance
apim3 <- gls(trigram_score_A ~ authenticity_A, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

apim3.b <- gls(trigram_score_A ~ authenticity_A + howbody_avg_A, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

apim3.c <- gls(trigram_score_A ~ authenticity_A + howbody_avg_A + a2pSOO_P, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

```{r}
#relationship agency
apim4 <- gls(relag_A ~ authenticity_A, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

apim4.b <- gls(relag_A ~ authenticity_A + howbody_avg_A, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

apim4.c <- gls(relag_A ~ authenticity_A + howbody_avg_A + a2pSOO_P, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

```{r}
#career aspirations
apim5 <- gls(careerasp_A ~ authenticity_A, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

apim5.b <- gls(careerasp_A ~ authenticity_A + howbody_avg_A, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

apim5.c <- gls(careerasp_A ~ authenticity_A + howbody_avg_A + a2pSOO_P, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

>>>>

While @garcia2016objectification used dyadic path analysis, we will conduct our dyadic analyses using multilevel modeling. Dyadic analyses for distingishable dyads (e.g., mixed-gender interacting pairs) is more natural in Structual Equation Modeling (SEM) than it is for indistinguishable dayds (e.g., same-gender interacting pairs) [@ledermann2017analyzing; @garcia2015moderation]. One reason for this asymmetry is that, due to the arbitrary distinctions made bewteen "partner 1" and "partner 2" in indistinguishable dyads, many estimates need to be fixed to be equal (i.e., paths, variances, covariances, endogenous intercepts, and exogenous means) for indistinguishable dyads but these equality contraints should not then be considered in the degrees of freedom calculations for fit estimations [@olsen2006structural]. Further, @olsen2006structural detail how a new independence model and the corresponding fit measure should be re-calculated for indistinguishable dyads models. The current study uses dyadic multilevel modeling (MLM) to test all relationships and mediation paterns. The online supplementary materials contains analysis using SEM. See @ledermann2017analyzing for a more complete discussion of the considerations for using SEM versus MLM for dyadic analysis.

@@

Before moving to the main analyses, we discuss statistical equivalence test that provide support for combining Sample 1 and Sample 2 in one analysis sample. The online supplemental material contains the main analyses separated by samples. All results presented below are from models including sample as a control variable.

@@

```{r}
#SSO
apim1 <- gls(howbody_avg_A ~ a2pSOO_A + a2pSOO_P + TSO_A + a2pSOO_P*TSO_A + smith_or_clark, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

apim1.b <- gls(howbody_avg_A ~ a2pSOO_A + a2pSOO_P + TSO_A + smith_or_clark, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

summary(apim1)
summary(apim1.b)
```
The most important finding from @garcia2016objectification was the significant partner effect of other objectification and SSO (specifically men's objectification of women and women's SSO). As expected, the partner effect of other-objectification on SSO in the current all-women sample was statistically signficant, `r report_stats(apim1, 3)`, replicating @garcia2016objectification's fiding. One's own other objectification had no effect on SSO, `r report_stats(apim1, 2)`. Contrary to past finding however, there was no statistically significant interaction of partner's other objectification and the person's trait self-objectification on SSO, `r report_stats(apim1, 5)`. There was also no significant main effect of trait self-objectification on SSO `r report_stats(apim1.b, 4)`.

```{r}
#authenticity
apim2 <- gls(authenticity_A ~ howbody_avg_A + smith_or_clark, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

apim2.b <- gls(authenticity_A ~ howbody_avg_A + a2pSOO_P + smith_or_clark, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

apim2.c <- gls(authenticity_A ~a2pSOO_P + smith_or_clark, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

```{r}
#cognitive performance
apim3 <- gls(trigram_score_A ~ authenticity_A + smith_or_clark, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

apim3.b <- gls(trigram_score_A ~ authenticity_A + howbody_avg_A + smith_or_clark, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

apim3.c <- gls(trigram_score_A ~ authenticity_A + howbody_avg_A + a2pSOO_P + smith_or_clark, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

```{r}
#relationship agency
apim4 <- gls(relag_A ~ authenticity_A + smith_or_clark, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

apim4.b <- gls(relag_A ~ authenticity_A + howbody_avg_A + smith_or_clark, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

apim4.c <- gls(relag_A ~ authenticity_A + howbody_avg_A + a2pSOO_P + smith_or_clark, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

```{r}
#career aspirations
apim5 <- gls(careerasp_A ~ authenticity_A + smith_or_clark, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

apim5.b <- gls(careerasp_A ~ authenticity_A + howbody_avg_A + smith_or_clark, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

@@

apim5.c <- gls(careerasp_A ~ authenticity_A + howbody_avg_A + a2pSOO_P + smith_or_clark, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID),
                 data=clarksmith_women)

### 2020-07-09 Final_Manuscript.tex
small changes closing github issues

There were some similar correaltions bewtween study variables across
samples.

@@

The most important finding from Garcia et al. (2016) was the significant
partner effect of other objectification and SSO (specifically men's
objectification of women and women's SSO). As expected, the partner
effect of other-objectification on SSO in the current all-women sample
was statistically signficant, \emph{b} = 0.29, \emph{SE} = 0.12,
\emph{p} = .017, replicating Garcia et al. (2016)'s fiding. One's own
other objectification had no effect on SSO, \emph{b} = -0.16, \emph{SE}
= 0.12, \emph{p} = .193. Contrary to past finding however, there was no
statistically significant interaction of partner's other objectification
and the person's trait self-objectification on SSO, \emph{b} = -0.02,
\emph{SE} = 0.04, \emph{p} = .589. There was also no significant main
effect of trait self-objectification on SSO \emph{b} = 0.07, \emph{SE} =
0.05, \emph{p} = .170.

Contrary to expectations, there was no significant effect of SSO on
interaction authenticity, although the estimate of this effect was in
the hypothesized negative direction, \emph{b} = -0.09, \emph{SE} = 0.11,
\emph{p} = .415. Because authenticity was a composite score of 9 items,
two of which were interaction specific authenticity items, we also
tested the effect of SSO on these items individually\ldots{}ADD
ANALYSIS\ldots{}Although we hypothesized that SSO would mediate the
relationship between partner's other objectification and interaction
authenticity, after finding no relationship bewteen SSO and authencity,
we also tested if the partner's other objectification had a direct
effect on authenticity, but this effect was not significant, \emph{b} =
0.05, \emph{SE} = 0.11, \emph{p} = .662 (nor was the total effect of
partner's other objectification on authenticity, \emph{b} = 0.02,
\emph{SE} = 0.1, \emph{p} = .855).

Lastly, althought there was no evidence that SSO was related to
interaction authenticity in the current sample, we tested if interaction
authenticity (composite of nine items) had effects on cognitive
performace, career aspirations, and relationship agency, as it did in
Garcia et al. (2016). We again used MLM and thus, these efefcts were
tested in three separate models. There was no significant effect of
interaction authenticity on cognitive performance, \emph{b} = 0.31,
\emph{SE} = 0.28, \emph{p} = .262, but authenticity was significantly
positively related to both career aspirations, \emph{b} = 0.19,
\emph{SE} = 0.07, \emph{p} = .009, and relationships agency, \emph{b} =
0.23, \emph{SE} = 0.12, \emph{p} = .048. There was no direct effect of
SSO on cognitive performance, \emph{b} = 0.05, \emph{SE} = 0.25,
\emph{p} = .846, and no direct effect of partner's other objectificaiton
on cognifitve performance, \emph{b} = 0.03, \emph{SE} = 0.26, \emph{p} =
.900. There was no direct effect of SSO on career aspirations, \emph{b}
= 0.03, \emph{SE} = 0.06, \emph{p} = .653, and no direct effect of
partner's other objectificaiton on career aspirations, \emph{b} = -0.05,
\emph{SE} = 0.06, \emph{p} = .405. There was no direct effect of SSO on
relationship agency, \emph{b} = -0.04, \emph{SE} = 0.11, \emph{p} =
.699, and no direct effect of partner's other objectificaiton on
relationship agency, \emph{b} = -0.07, \emph{SE} = 0.1, \emph{p} = .474.

>>>>

@@

The most important finding from Garcia et al. (2016) was the significant
partner effect of other objectification and SSO (specifically men's
objectification of women and women's SSO). As expected, the partner
effect of other-objectification on SSO in the current all-women sample
was statistically signficant, \emph{b} = 0.29, \emph{SE} = 0.12,
\emph{p} = .019, replicating Garcia et al. (2016)'s fiding. One's own
other objectification had no effect on SSO, \emph{b} = -0.16, \emph{SE}
= 0.12, \emph{p} = .210. Contrary to past finding however, there was no
statistically significant interaction of partner's other objectification
and the person's trait self-objectification on SSO, \emph{b} = 0.03,
\emph{SE} = 0.27, \emph{p} = .910. There was also no significant main
effect of trait self-objectification on SSO \emph{b} = 0.07, \emph{SE} =
0.05, \emph{p} = .183.

Contrary to expectations, there was no significant effect of SSO on
interaction authenticity, although the estimate of this effect was in
the hypothesized negative direction, \emph{b} = -0.09, \emph{SE} = 0.12,
\emph{p} = .431. Because authenticity was a composite score of 9 items,
two of which were interaction specific authenticity items, we also
estimated the pairwise correlations bewteen SSO and all these items
individually. They were all small, ranging from only -0.01 to -0.14.
Although we hypothesized that SSO would mediate the relationship between
partner's other objectification and interaction authenticity, after
finding no relationship bewteen SSO and authencity, we also tested if
the partner's other objectification had a direct effect on authenticity,
but this effect was not significant, \emph{b} = 0.06, \emph{SE} = 0.12,
\emph{p} = .608 (nor was the total effect of partner's other
objectification on authenticity, \emph{b} = 0.03, \emph{SE} = 0.11,
\emph{p} = .787).

Lastly, althought there was no evidence that SSO was related to
interaction authenticity in the current sample, we tested if interaction
authenticity (composite of nine items) had effects on cognitive
performace, career aspirations, and relationship agency, as it did in
Garcia et al. (2016). We again used MLM and thus, these efefcts were
tested in three separate models. There was no significant effect of
interaction authenticity on cognitive performance, \emph{b} = 0.32,
\emph{SE} = 0.28, \emph{p} = .258, but authenticity was significantly
positively related to both career aspirations, \emph{b} = 0.18,
\emph{SE} = 0.07, \emph{p} = .010, and relationships agency, \emph{b} =
0.23, \emph{SE} = 0.12, \emph{p} = .049. There was no direct effect of
SSO on cognitive performance, \emph{b} = 0.04, \emph{SE} = 0.25,
\emph{p} = .872, and no direct effect of partner's other objectificaiton
on cognifitve performance, \emph{b} = 0.01, \emph{SE} = 0.27, \emph{p} =
.962. There was no direct effect of SSO on career aspirations, \emph{b}
= 0.03, \emph{SE} = 0.06, \emph{p} = .657, and no direct effect of
partner's other objectificaiton on career aspirations, \emph{b} = -0.06,
\emph{SE} = 0.07, \emph{p} = .378. There was no direct effect of SSO on
relationship agency, \emph{b} = -0.05, \emph{SE} = 0.11, \emph{p} =
.659, and no direct effect of partner's other objectificaiton on
relationship agency, \emph{b} = -0.1, \emph{SE} = 0.11, \emph{p} = .365.
